%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% %
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%
\Extrachap{FURTHER READING}

\biblstarthook{}


\begin{thebibliography}{99.}%


\bibitem{ARTIN} ARTIN, E.: ``The Gamma Function,'' Holt, Rinehart and Winston, Inc., New York, 1964.
\bibitem{BOAS} BOAS, R. P.: ``A Primer of Real Functions,'' Carus Mathematical Monograph No. 13, John Wiley \& Sons, Inc., New York, 1960.
\bibitem{BUCKANALYSIS} BUCK, R. C. (ed.): ``Studies in Modern Analysis,'' Prentice-Hall, Inc., Englewood Cliffs, N.J., 1962.
\bibitem{BUCKCALCULUS} BUCK, R. C. (ed.): ``Advanced Calculus'' 2d ed., McGraw-Hill Book Company, New York, 1965.
\bibitem{BURKILL} BURKILL, J. C.: ``The Lebesgue Integral,'' Cambridge University Press, New York, 1951.
\bibitem{DIEUDONNE} DIEUDONNE, J.: ``Foundations of Modern Analysis,'' Academic Press, Inc., New York, 1960.
\bibitem{FLEMING} FLEMING, w. H.: ``Functions of Several Variables,'' Addison-Wesley Publishing Company, Inc., Reading, Mass., 1965.
\bibitem{GRAVES} GRAVES, L. M.: ``The Theory of Functions of Real Variables,'' 2d ed., McGraw-Hill Book Company, New York, 1956.
\bibitem{HALMOSMEASURE} HALMOS, P. R.: ``Measure Theory,'' D. Van Nostrand Company, Inc., Princeton, N.J., 1950.
\bibitem{HALMOSVECTOR} HALMOS, P. R.: ``Finite-dimensional Vector Spaces,'' 2d ed., D. Van Nostrand Company, Inc., Princeton, N.J., 1958.
\bibitem{HARDYPURE} HARDY, G. H.: ``Pure Mathematics,'' 9th ed., Cambridge University Press, New York, 1947.
\bibitem{HARDYFOURIER} HARDY, G. H. and ROGOSINSKI, W.: ``Fourier Series,'' 2d ed., Cambridge University Press, New York, 1950.
\bibitem{HERSTEIN} HERSTEIN, I. N.: ``Topics in Algebra,'' Blaisdell Publishing Company, New York, 1964.
\bibitem{HEWITT} HEWITT, E., and STROMBERG, K. : ``Real and Abstract Analysis,'' Springer Publishing Co., Inc., New York, 1965.
\bibitem{KELLOGG} KELLOGG, O. D.: ``Foundations of Potential Theory,'' Frederick Ungar Publishing Co., New York, 1940.
\bibitem{KNOPP} KNOPP, K.: ``Theory and Application of Infinite Series,'' Blackie \& Son, Ltd., Glasgow, 1928.
\bibitem{LANDAU} LANDAU, E. G. H.: ``Foundations of Analysis,'' Chelsea Publishing Company, New York, 1951.
\bibitem{MCSHANE} MCSHANE, E. J.: ``Integration,'' Princeton University Press, Princeton, N.J., 1944.
\bibitem{NIVEN} NIVEN, I. M.: ``Irrational Numbers,'' Carus Mathematical Monograph No. 11, John Wiley \& Sons, Inc., New York, 1956.
\bibitem{ROYDEN} ROYDEN, H. L.: ``Real Analysis,'' The Macmillan Company, New York, 1963.
\bibitem{RUDIN} RUDIN, W.: ``Real and Complex Analysis,'' 2d ed., McGraw-Hill Book Company, New York, 1974.
\bibitem{SIMMONS} SIMMONS, G. F.: ``Topology and Modern Analysis,'' McGraw-Hill Book Company, New York, 1963.
\bibitem{SINGER} SINGER, 1. M., and THORPE, J. A.: ``Lecture Notes on Elementary Topology and Geometry,'' Scott, Foresman and Company, Glenview, Ill., 1967.
\bibitem{SMITH} SMITH, K. T.: ``Primer of Modern Analysis'' Bogden and Quigley, Tarrytown-on-Hudson, N.Y., 1971.
\bibitem{SPIVAK} SPIVAK, M.: ``Calculus on Manifolds,'' W. A. Benjamin, Inc., New York, 1965.
\bibitem{THURSTON} THURSTON, H. A.: ``The Number System,'' Blackie \& Son, Ltd., London-Glasgow, 1956.




\end{thebibliography}
